Nail: A practical interface generator for data formats

### 2014-04-01 paper/intro.tex
small intro tweaks

This paper presents the initial design and implementation of Nail, a parser
generator that greatly reduces the programmer effort required to use a
grammar-based parser. Nail addresses the above three challenges with several key
ideas. First, Nail reduces the expressiveness of its grammar language by
removing semantic actions. Existing parser generators allow arbitrary
computation to transform between the AST and the parser output.%  Instead, Nail
% derives the structure of its output automatically from the grammar, forcing the
% programmer to clearly separate syntactic validation and semantic processing.

Second, this allows the parser to construct a \emph{syntactic bijection} between input
and output. That is, parsing is the inverse of generating output. However,
Nail allows \emph{constants} in the external format to have multiple
representations if they should not affect the semantics of the data. For
example, in a text protocol, the amount of white-space separating tokens should
not affect the meaning of the data and is consequently not exposed to the
application by Nail in the internal representation. However, as long as
constants are only used for their intended purpose of representing syntax-only
features, the generated output will have the same semantics as the parsed input.

>>>>

This paper presents the initial design and implementation of Nail, a parser
generator that greatly reduces the programmer effort required to use a
grammar-based parser. Nail addresses the above three challenges with
several key ideas, as follows.

First, Nail reduces the expressiveness of its grammar language by
removing semantic actions. Although this limits the kinds of grammars that
Nail can support, compared to parser generators that allow arbitrary
computation in semantic actions, many widely used formats can be still
captured by Nail grammars, and the lack of arbitrary semantic actions
enables Nail to automate parsing input and producing output.

%  Instead, Nail
% derives the structure of its output automatically from the grammar, forcing the
% programmer to clearly separate syntactic validation and semantic processing.

Second, this allows the parser to construct a \emph{syntactic bijection}
between input and output---that is, parsing is the inverse of generating
output.  The bijection does not guarantee that all aspects of the data
format are preserved; for example, in a text protocol, the amount of
white-space separating tokens should not affect the meaning of the
data, and is consequently not exposed to the application by Nail in the
internal representation.  More generally, Nail allows \emph{constants}
in the external format to have multiple representations if they do not
affect the semantics of the data.  As long as constants are only used
for their intended purpose of representing syntax-only features, the
generated output will have the same semantics as the parsed input.
